---
title: "Prevalencia y desigualdades sociales en factores de riesgo de enfermedad cardiovascular - `r nombre_ca[v]`"
subtitle: "Proyecto PI21/01868" 
output: powerpoint_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  dev = "svg",
  fig.width = 14,
  fig.height = 10
)
```

# Diabetes

## Prevalencias

```{r, echo=F}

fig_1 + theme(text = element_text(size = 18),
              axis.text.y = element_text(size = 18),
              axis.title.y = element_text(size = 18),
              axis.title.x = element_text(size = 18),
              axis.text.x = element_text(size = 14),
              legend.text = element_text(size = 18),
              strip.text = element_text(size = 18))

```

## Desigualdades

```{r, echo=F}

fig_2 + theme(text = element_text(size = 18),
              axis.text.y = element_text(size = 18),
              axis.title.y = element_text(size = 18),
              axis.title.x = element_text(size = 18),
              axis.text.x = element_text(size = 14),
              legend.text = element_text(size = 18),
              strip.text = element_text(size = 18))

```

# Hipertensión arterial

## Prevalencias

```{r, echo=F}

fig_3 + theme(text = element_text(size = 18),
              axis.text.y = element_text(size = 18),
              axis.title.y = element_text(size = 18),
              axis.title.x = element_text(size = 18),
              axis.text.x = element_text(size = 14),
              legend.text = element_text(size = 18),
              strip.text = element_text(size = 18))

```

## Desigualdades

```{r, echo=F}

fig_4 + theme(text = element_text(size = 18),
              axis.text.y = element_text(size = 18),
              axis.title.y = element_text(size = 18),
              axis.title.x = element_text(size = 18),
              axis.text.x = element_text(size = 14),
              legend.text = element_text(size = 18),
              strip.text = element_text(size = 18))

```

# Hipercolesterolemia

## Prevalencias

```{r, echo=F}

fig_5 + theme(text = element_text(size = 18),
              axis.text.y = element_text(size = 18),
              axis.title.y = element_text(size = 18),
              axis.title.x = element_text(size = 18),
              axis.text.x = element_text(size = 14),
              legend.text = element_text(size = 18),
              strip.text = element_text(size = 18))

```

## Desigualdades

```{r, echo=F}

fig_6 + theme(text = element_text(size = 18),
              axis.text.y = element_text(size = 18),
              axis.title.y = element_text(size = 18),
              axis.title.x = element_text(size = 18),
              axis.text.x = element_text(size = 14),
              legend.text = element_text(size = 18),
              strip.text = element_text(size = 18))

```

# Obesidad

## Prevalencias

```{r, echo=F}

fig_7 + theme(text = element_text(size = 18),
              axis.text.y = element_text(size = 18),
              axis.title.y = element_text(size = 18),
              axis.title.x = element_text(size = 18),
              axis.text.x = element_text(size = 14),
              legend.text = element_text(size = 18),
              strip.text = element_text(size = 18))

```

## Desigualdades

```{r, echo=F}

fig_8 + theme(text = element_text(size = 18),
              axis.text.y = element_text(size = 18),
              axis.title.y = element_text(size = 18),
              axis.title.x = element_text(size = 18),
              axis.text.x = element_text(size = 14),
              legend.text = element_text(size = 18),
              strip.text = element_text(size = 18))

```

# Sedentarismo

## Prevalencias

```{r, echo=F}

fig_9 + theme(text = element_text(size = 18),
              axis.text.y = element_text(size = 18),
              axis.title.y = element_text(size = 18),
              axis.title.x = element_text(size = 18),
              axis.text.x = element_text(size = 14),
              legend.text = element_text(size = 18),
              strip.text = element_text(size = 18))

```

## Desigualdades

```{r, echo=F}

fig_10 + theme(text = element_text(size = 18),
              axis.text.y = element_text(size = 18),
              axis.title.y = element_text(size = 18),
              axis.title.x = element_text(size = 18),
              axis.text.x = element_text(size = 14),
              legend.text = element_text(size = 18),
              strip.text = element_text(size = 18))

```

# Tabaquismo

## Prevalencias

```{r, echo=F}

fig_11 + theme(text = element_text(size = 18),
              axis.text.y = element_text(size = 18),
              axis.title.y = element_text(size = 18),
              axis.title.x = element_text(size = 18),
              axis.text.x = element_text(size = 14),
              legend.text = element_text(size = 18),
              strip.text = element_text(size = 18))

```

## Desigualdades

```{r, echo=F}

fig_12 + theme(text = element_text(size = 18),
              axis.text.y = element_text(size = 18),
              axis.title.y = element_text(size = 18),
              axis.title.x = element_text(size = 18),
              axis.text.x = element_text(size = 14),
              legend.text = element_text(size = 18),
              strip.text = element_text(size = 18))

```

# Consumo de alcohol

## Prevalencias

```{r, echo=F}

fig_13 + theme(text = element_text(size = 18),
              axis.text.y = element_text(size = 18),
              axis.title.y = element_text(size = 18),
              axis.title.x = element_text(size = 18),
              axis.text.x = element_text(size = 14),
              legend.text = element_text(size = 18),
              strip.text = element_text(size = 18))

```

## Desigualdades

```{r, echo=F}

fig_14 + theme(text = element_text(size = 18),
              axis.text.y = element_text(size = 18),
              axis.title.y = element_text(size = 18),
              axis.title.x = element_text(size = 18),
              axis.text.x = element_text(size = 14),
              legend.text = element_text(size = 18),
              strip.text = element_text(size = 18))

```

# Alimentación

## Prevalencias

```{r, echo=F}

fig_15 + theme(text = element_text(size = 18),
              axis.text.y = element_text(size = 18),
              axis.title.y = element_text(size = 18),
              axis.title.x = element_text(size = 18),
              axis.text.x = element_text(size = 14),
              legend.text = element_text(size = 18),
              strip.text = element_text(size = 18))

```

## Desigualdades

```{r, echo=F}

fig_16 + theme(text = element_text(size = 18),
              axis.text.y = element_text(size = 18),
              axis.title.y = element_text(size = 18),
              axis.title.x = element_text(size = 18),
              axis.text.x = element_text(size = 14),
              legend.text = element_text(size = 18),
              strip.text = element_text(size = 18))

```